Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-03-06 src/tex/ms.tex
fix review bold format

\rev{
\subsubsection{Bayesian Evidence and the Influence of Priors}\label{sec:discussion-bayes}}
Our semi-analytical analysis (Section~\ref{sec:results-semianalytical}) employs Bayes factors to quantify the evidence in favor of or against the UV~Threshold Hypothesis that future observations may provide.
%In contrast to frequentist p-value tests, which only assess the likelihood of the null hypothesis, this approach explicitly incorporates the likelihood of the alternative hypothesis.
%However, Bayes factor analysis limits the scope to two competing hypotheses, and it does not estimate posterior probabilities.
}

>>>>

\subsubsection{\rev{Bayesian Evidence and the Influence of Priors}}\label{sec:discussion-bayes}
\rev{Our semi-analytical analysis (Section~\ref{sec:results-semianalytical}) employs Bayes factors to quantify the evidence in favor of or against the UV~Threshold Hypothesis that future observations may provide.}
%In contrast to frequentist p-value tests, which only assess the likelihood of the null hypothesis, this approach explicitly incorporates the likelihood of the alternative hypothesis.
%However, Bayes factor analysis limits the scope to two competing hypotheses, and it does not estimate posterior probabilities.
